Recursive Neural Network Part-of-Speech Tagger

### 2013-12-21 paper/paper.tex
Add two figures and one citation. Describe back propagation through time.

@@

TODO: Describe back propagation through time.

@@

>>>>

\begin{figure}
	\includegraphics[scale=0.3]{model_figure.png}
	\caption{Recursive Neural Network Model}\label{Model_fig}
\end{figure}

@@

Backpropagation through time is a technique to run backpropagation against recursive neural networks, which include cyclic connections. We perform backpropagation through time automatically by running standard backpropagation against our unrolled recursive neural network with shared weight matrices. Each gradient update to the weight matrix is independently accumulated, resulting in the correct overall update. We perform the gradient update in minibatches, where a single sentence is a mini batch of tagged words and we simultaneously accumulate the errors for each of the words as we backpropogate. See Figure \ref{Bptt_fig} (Mikolov, 2012).

\begin{figure}
	\includegraphics[scale=0.5]{bptt.png}
	\caption{Back Propagation Through Time (Mikolov, 2012)}\label{Bptt_fig}
\end{figure}

@@

\bibitem[\protect\citename{Mikolov}2012]{Mikolov:12}
Tomáš~Mikolov.
\newblock 2012.
\newblock Statistical Language Models Based on Neural Networks.
\newblock {\em Diss. Ph. D. thesis, Brno University of Technology}.
